Commit Rater

### 2015-08-26 presentations/paper/methodology.tex
Transition smoothly from data processing to data synthesis
Remove some already finished todos
Fix spelling, mostly Marco's

Several repositories were chosen as sample sources, for the sake of having enough data to analyze in section\ref{sec:data-analysis}. Additionally, the authors of these repositories have different levels of being aware of and adhering to Git's commit message guidelines\cite{OffGuide}, which leads to a large spread of ratings accross them.

@@

Almost all of the criteria below relate to the commit message, only one of them states a very superficial rule about the changes in the commit. None of them process the code itself, neither inside the changes nor in the the code-base before or after applying the commit, as such criteria would require very language-specific knowledge that would have to be manually implemented for each desired language. By keeping our criteria language-independent, they remain applicable to all Git repositories.

In general, commit messages should consist of a subject line and a body \footnote{See \cite{OffGuide} for an exhaustive explanation and an example}. \cite{CB} summarizes the most important guidelines very nicely, and the first seven criteria below are directly taken or inspired from the blog post. Note that the seventh mentioned rule could not be made into a criterion, since it would require actual understanding of the commit message. Omitting this rule, we still infered one additional criterium (\ref{subs:body_used}) that we found missing in the list.

@@

Additionally, large subject lines might hint at having done more than one thing in a commit, since the author needs more space to explain what the commit does. Logically separating changesets is another rule from \cite{OffGuide}, which of course cannot be evaluated without great language-specific effort.

@@

\subsubsection{no\_long\_message}
\label{subs:no_long_message}
The subject line should be limited to less than 10 words. This is an extension of the subject\_limit criterion in \ref{subject_limit}, which might rarely allow 10 or more words. The reasoning behind this criterion is agein, that many words hint at more than one logical changeset in one commit. Also, concision should help making a message more easily understandable and scanning a log for a particular commit takes less effort. If there is need for longer explanations, they should be moved to the body.

@@

\subsubsection{no\_bulk\_change}
\label{subs:no_bulk_change}
Large changesets hint at a commit with more than one logical changeset. If 10 or more files are changed by a commit, chances are that that commit should have been divided into multiple commits. Furthermore, even a commit with 10 or more changes only contains one logical changeset, this hints at bad software architecture, altough this should maybe not be reflected in the evaluation of commits.

@@

This criterion is hugely problematic. In principle, spell checking is easily done with one of many libraries \footnote{We use GNU Aspell, via \url{https://metacpan.org/pod/Text::Aspell}}, but such libraries will report technical terms as errors and since we cannot manualy whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to 2. This will of course sometimes hide real errors. Maybe further research could provide an adequate solution to this problem or at least analyse the precision of applying a standard spell checker to very domain specific texts.

@@

The rate of how many of the commits pass a certain criterion may be interpreted as the rate with wich the author adheres the corresponding rule. The rate is calculated with the following formula:

@@

The important thing to note about this formula is, that it excludes $undef$. This means, that for instance authors who rarely use the body (see \ref{subs:body_used}) still have a useful refelction on how many of their commits with body were limited to 72 characters per line (\ref{subs:body_limit}).

@@

\subsubsection{Repository-level}
The analysis on this level is very similar to the analyis on the author-level. It would have been easy to just aggregate the triples of all authors in a repo and apply equation \ref{eq:weightedAverage} to reiceive an average for the whole repository. But we decided that this would serve no practical purpose, since the distribution over the behaviour of many authors across all criteria would likely have a very high variance and only very general trends could be infered from the results.

Instead, on this level we opted to create boxplots with the rates for each criterion for all authors. Since each author has one triple per ciriterion, this means that for example a repository with 100 authors has 100 datapoints (rates) for a boxplot. The boxplots will be shown and discussed in \ref{sec:results}.

\subsubsection{Above repository-level}
It may be of further interest to look at the averages of adherance to guidelines across multiple repos and thereby extrapolate some general statistics about ueage of the guidelines in the Git community. But we did not concern ourselves with this level, since we found it to be unrelated to our research questions.

>>>>

Several repositories were chosen as sample sources, for the sake of having enough data to analyze in section\ref{sec:data-analysis}. Additionally, the authors of these repositories have different levels of being aware of and adhering to Git's commit message guidelines\cite{OffGuide}, which leads to a large spread of ratings across them.

@@

Almost all of the criteria below relate to the commit message, only one of them states a very superficial rule about the changes in the commit. None of them process the code itself, neither inside the changes nor in the code-base before or after applying the commit, as such criteria would require very language-specific knowledge that would have to be manually implemented for each desired language. By keeping our criteria language-independent, they remain applicable to all Git repositories.

In general, commit messages should consist of a subject line and a body \footnote{See \cite{OffGuide} for an exhaustive explanation and an example}. \cite{CB} summarizes the most important guidelines very nicely, and the first seven criteria below are directly taken or inspired from the blog post. Note that the seventh mentioned rule could not be made into a criterion, since it would require actual understanding of the commit message. Omitting this rule, we still inferred one additional criterion (\ref{subs:body_used}) that we found missing in the list.

@@

Additionally, large subject lines might hint at having done more than one thing in a commit, since the author needs more space to explain what the commit does. Logically separating change sets is another rule from \cite{OffGuide}, which of course cannot be evaluated without great language-specific effort.

@@

\subsubsection{no\_long\_message}
\label{subs:no_long_message}
The subject line should be limited to less than 10 words. This is an extension of the subject\_limit criterion in \ref{subject_limit}, which might rarely allow 10 or more words. The reasoning behind this criterion is again, that many words hint at more than one logical change set in one commit. Also, concision should help making a message more easily understandable and scanning a log for a particular commit takes less effort. If there is need for longer explanations, they should be moved to the body.

@@

\subsubsection{no\_bulk\_change}
\label{subs:no_bulk_change}
Large change sets hint at a commit with more than one logical change set. If 10 or more files are changed by a commit, chances are that that commit should have been divided into multiple commits. Furthermore, even a commit with 10 or more changes only contains one logical change set, this hints at bad software architecture, although this should maybe not be reflected in the evaluation of commits.

@@

This criterion is hugely problematic. In principle, spell checking is easily done with one of many libraries \footnote{We use GNU Aspell, via \url{https://metacpan.org/pod/Text::Aspell}}, but such libraries will report technical terms as errors and since we cannot manually whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to 2. This will of course sometimes hide real errors. Maybe further research could provide an adequate solution to this problem or at least analyse the precision of applying a standard spell checker to very domain specific texts.

@@

The rate of how many of the commits pass a certain criterion may be interpreted as the rate with which the author adheres the corresponding rule. The rate is calculated with the following formula:

@@

The important thing to note about this formula is, that it excludes $undef$. This means, that for instance authors who rarely use the body (see \ref{subs:body_used}) still have a useful reflection on how many of their commits with body were limited to 72 characters per line (\ref{subs:body_limit}).

@@

\subsubsection{Repository-level}
The analysis on this level is very similar to the analysis on the author-level. It would have been easy to just aggregate the triples of all authors in a repo and apply equation \ref{eq:weightedAverage} to receive an average for the whole repository. But we decided that this would serve no practical purpose, since the distribution over the behaviour of many authors across all criteria would likely have a very high variance and only very general trends could be inferred from the results.

Instead, on this level we opted to create boxplots with the rates for each criterion for all authors. Since each author has one triple per criterion, this means that for example a repository with 100 authors has 100 data points (rates) for a boxplot. The boxplots will be shown and discussed in \ref{sec:results}.

\subsubsection{Above repository-level}
It may be of further interest to look at the averages of adherence to guidelines across multiple repos and thereby extrapolate some general statistics about usage of the guidelines in the Git community. But we did not concern ourselves with this level, since we found it to be unrelated to our research questions.
